---
title: "Analysis on Wine Reviews"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include=FALSE}
library(prettydoc)
library(data.table)
library(DT)
library(tidyverse)
library(tm)
library(stringr)
library(quanteda)
library(irlba)
library(ggplot2)
library(caret)
library(recommenderlab)
library(Hmisc)
library(wordcloud)
library(wordcloud2)
```

```{r read data, echo=FALSE}
dat <- fread(input = "wines.csv",verbose = FALSE,na.strings=c(""))
dat=dat[,-1]
```


```{r functions}
percentage.table <- function(x, digits = 1){
  tab <- table(x)
  percentage.tab <- 100*tab/(sum(tab))
  rounded.tab <- round(x = percentage.tab, digits = digits)
  return(rounded.tab)
}
round.numerics <- function(x, digits){
  if(is.numeric(x)){
    x <- round(x = x, digits = digits)
  }
  return(x)
}
miss.value <- function(x){
  miss.rate <- round(100*mean(is.na(x)),2)
  return(miss.rate)
}
get.unique = function(x){
  ux=length(unique(x))
  return(ux)
}
```


```{r constants, include=F}
country.name <- "country"
description.name <- "description"           
designation.name <- "designation"           
points.name <- "points"               
price.name <- "price"                 
province.name <- "province"              
region_1.name <- "region_1"              
region_2.name <- "region_2"             
taster.name <- "taster_name"           
twitter.name <- "taster_twitter_handle" 
title.name <- "title"                 
variaty.name <- "variety"              
winery.name <- "winery"               
dat[,eval(points.name)] <- as.numeric(dat[,get(points.name)])
dat[,eval(price.name)] <- as.numeric(dat[,get(price.name)])
single.var <- c(points.name, price.name, country.name)
```

# Introduction

<p>One of the most important research questions in the wine related area is the ranking, rating and judging of wine[1]. In the past, the research on these problems manily utilized samll dataset[2]. However, with data science techniques, we are able to investigate the problem using large amount of data. </p>

<p>Majority of the studies focus on analyzing physicochemical laboratory wine data, while little research has been conducted on the content of wine reviews. Mining useful information from wine reviews and tasters preferences can provide new insights from a consumer perspective. Therefore, it is meaningful to untilize these data and generate better wine recommendations.</p>


# Source of Data
<body>
We used <b> <a href = "https://www.kaggle.com/zynicide/wine-reviews" > Wine Reviews</a></b> data which was scraped from <i>WineEntusiast</i> website on November 22nd, 2017 by @zackthoutt on Kaggle. The orginial data also had an index variable which we ignored here since it has no impact on our project. There are 13 variables in total:

<ul>
<li><b>Country</b>: The country that the wine is from; </li>

<li><b>Description</b>: wine reviews; </li>

<li><b>Designation</b>: The vineyard within the winery where the grapes that made the wine are from;</li>

<li><b>Points</b>: The number of points WineEnthusiast rated the wine on a scale of 1-100 (though they say they only post reviews for wines that score >=80);</li>

<li><b>Price</b>: The cost for a bottle of the wine; </li>

<li><b>Province</b>: The province or state that the wine is from;</li>

<li><b>Region_1</b>: The wine growing area in a province or state (ie Napa) ;</li>

<li><b>Region_2</b>: Sometimes there are more specific regions specified within a wine growing area (ie Rutherford inside the Napa Valley), but this value can sometimes be blank ;</li>

<li><b>Taster_name</b>: Name of the taster(reviewer);</li>

<li><b>Taster_twitter_handle</b>;</li>

<li><b>Title</b>: The title of the wine review, which often contains the vintage if you're interested in extracting that feature ;</li>

<li><b>Variety</b>: The type of grapes used to make the wine (ie Pinot Noir) ;</li>

<li><b>Winery</b>: The winery that made the wine.</li>

</ul>
</body>

```{r,include=F}
datatable(dat[1:5,])
```

# Examination of the Data

<p>We first checked the missing vlaues in the data and visualize the percentage of that for each varible. **Country, province, region_1 and region_2** are varibales giving geographic information about the wine, since the majority of **region_2** and 16.4% of **region_1** are missing, we choose to focus on **country** unless more detailed geographic information are needed.</p>

We then examined the unique values for each varible. **Designation, winery, title** have many unique values, hence we decided to treat them as random effects but not predictors when modeling.<br>

**Price** of the wine ranges from 4 to 3300 with some extreme values. We then visualized **price** in the report enginee and recommended a way to define price range (<10, 10~30, 30~50, 50~200, 200~500, >500)

Variable **points** ranges from 80 to 100. Its distribution was close to a bell shape. <br>

**Description, taster_name** and **taster_twitter_handle** provides information about the taster and their reviews on the wine. We examined these variables later based on the needs for text anlysis and recommendation systems building.

```{r percentage missing}
tab <- dat[,lapply(X=.SD,FUN="miss.value"),.SD=names(dat)[-1]]
tab2 <- data.table(var=names(dat[,-1]),miss=as.numeric(tab))
# create a plot of all the missing rate 
barplot(height=tab2$miss, names.arg=tab2$var,space=0.01, las=1, main="Percentage of Missing Value",ylab="Percentage", ylim=c(0,80),col=rainbow(13),border="white")
text(x = -0.5 + 1.02*1:tab2[, .N], y = -15, labels = tab2$var,srt = 45)
space_val=0
text(x=-0.4+1:length(tab)*(1+space_val),y=tab,labels=sprintf("%.1f%%",tab),pos=3)

#number of unique values for each variable
unitab=dat[,lapply(.SD,FUN="get.unique")]
datatable(unitab)
#range of price
summary(dat$price)
hist(dat[,price],xlab="price", col= "#85C1E9", border="white", main="Histogram of price")
#points plot
hist(dat$points,xlab="points", col= "#85C1E9", border="white", main="Histogram of points")
```


# Investigation:
##1. Sentiment Analysis 
###Overview of *Description*

Suppose we are exploring sales status of different wines in our website. What do we care about most? The answer might be the *Final Point* the testers give out. But some reality need to be considered. 
First of all, the dataset we have only includes data with points above 80. Comparing to our scoring scale, which is 0-100, scores from 80 to 100 have a strong indication that the testers are relatively like this kind of wine. Under this circumstance, how can we specify the difference among them? 
Second, when customers evaluate a product, their evaluation objects vary. Some people focus on the taste while others prefer the looks and smell. As what we get from Final Point is just the final evaluation, we cannot tell which aspect this tester pay attention to. However, when recommending product to users, it could be more precise if you know about his or her preference on which aspect he or she focuses on. 
From the reason above, *Final Point* is not enough for us to make an accurate conclusion on customers exact evaluation on this type of wine. Thus, we should take a look at *Description* ,which gives us more details.
In order to analyze this text variable, we first take a look at the words' length. We split every sentence into words and draw a distribution of words' length. We find that it is close to a normal distribution with mean is roughly 45 words per description, which is a good start.

```{r distributioin of words length}
ggplot(data = subdat, aes(x = descriptioncount)) + geom_histogram(bins=30, fill = 'royalblue4') + 
 theme_classic() +
 ggtitle('Description word length Distribution') + 
 xlab('Number of words used in Description') + 
 ylab('Number of Observations') + 
 theme(plot.title = element_text(hjust = 0.5)) + scale_fill_brewer(palette = "Blues")
 ylim(0,25000) 
```

To give a accurate evaluation, we start from estimating sentiment behind descriptioin, which is sentiment analysis.
There's a default classification criteria of "negative" and "positive", which helps us to roughly divide description into two categories. From the result,we get more positive descriptions than negative one which kind of makes sense because we just use data with points from 80 to 100. There, the proportion of positive description is 79% and that of negative description is roughly 21%.
The result kind of shows discrepancy. As we mention above, we shift data with points above 80, which is a relatively higher score with scale from 0 to 100. We didn't expect negative description that much. In order to have a more realistic understanding of the result, we create a new scale which is from 80 to 100 and we assume points above 90 is "positive" points while points below 90 is "negative" points.Thus, we make a prediction the distribution of new-scaled points is consistent with the description of negative and positive. However, from what we get we conclude that the prediction is not correct, which indicates that although the final point is positive, we still have negative desription. Thus, it's necessary to analyze description with more specific classification which is text analysis.

```{r sentiment analysis}
subdat %>%
unnest_tokens(output = word, input = description) %>%
inner_join(get_sentiments('bing')) %>%
group_by(sentiment) %>%
count() %>%
ggplot(aes(x=sentiment,y=n, fill=sentiment)) + geom_col() + 
 theme_classic() + guides(fill=F) + 
  scale_fill_brewer(palette = "Accent")+
  ggtitle('Sentiment Distribution') + ylab('Number of Oversation') + 
  ylim(0,400000) + theme(plot.title = element_text(hjust = 0.5)) 
```


##Sentiment analysis of different countries

There are two main factors which influence the quality of a type of wine, one is natural cause and one is man-made cause. The country of origin is the important component in natural cause. Thus, we want to specify if wines from different countries will have different descriptions from testers. With the sentiment perspective, it will be shown as the difference in the distribution of negative and positive sentiment in description.
Then, we draw a graph of sentiment distribution to see the difference among wines from different counties. As some countries’ wine do not have sufficient recorded review, we just show countries with large amount of data. 
From the result, we can tell that there exists difference among countries. Meanwhile, wines that from most of the famous places like, France, South Africa have the larger proportion of positive description which is consistent with our intuition.

```{r }
data1 <- subdat[,length(get(description.name)),by=country.name]
setorderv(data1,cols = "V1",-1)
order1 <- data1$country[1:15]

subdat[get(country.name)%in%order1,] %>%
unnest_tokens(output = word, input = description) %>%
inner_join(get_sentiments('bing')) %>%
group_by(country,sentiment) %>%
summarise(n = n())%>%
mutate(proportion = n/sum(n)) %>%
ggplot(aes(x= country , y=proportion,fill=sentiment)) + geom_col() + 
 theme_classic() + guides(fill=F) + coord_flip() + 
  scale_fill_brewer(palette = "Accent")+
 ggtitle('Sentiment Distribution') + ylab('Number of Obversation') + 
 theme(plot.title = element_text(hjust = 0.5)) 
```

##Other interesting finding

Dividing sentiment in "negative" and "positive" is somewhat sketchy and we have other way to make a more specific classfication. We extract more emotions from descriptions such as "disgust","joy" etc. To our surprise, there exists words containing sentiment like "anger","sad" which seems a little bit strange in a wine description. This interesting finding gives us more hint on our further text analysis.

```{r}
subdat %>%
unnest_tokens(output = word, input = description) %>%
inner_join(get_sentiments('nrc')) %>%
group_by(sentiment) %>%
count() %>%
ggplot(aes(x=reorder(sentiment,-n),y=n, fill=sentiment)) + geom_col() + 
 theme_grey() + guides(fill=F) + 
 ggtitle('Sentiment Distribution') + ylab('Number of Obversation') + 
 theme(plot.title = element_text(hjust = 0.5)) + xlab('Sentiment: Emotion') + 
  geom_text(aes(label = n),vjust = -.5, nudge_y = 1.4)

subdat %>%
unnest_tokens(output = word, input = description) %>%
inner_join(get_sentiments('nrc')) %>%
group_by(country,sentiment) %>%
summarise(n = n()) %>%
mutate(proportion = n/sum(n)) %>%
ggplot(aes(x= country, y=proportion,fill=sentiment, col = sentiment)) + geom_col() + 
 theme_classic() + guides(fill=F) + coord_flip() + 
 ggtitle('Sentiment Distribution') + ylab('Number of Oversation') + 
 theme(plot.title = element_text(hjust = 0.5))


subdat %>%
unnest_tokens(output = word, input = description) %>%
inner_join(get_sentiments('nrc')) %>%
 group_by(sentiment,points) %>%
 count()%>%
 group_by(sentiment, points) %>%
 summarise(n = mean(n)) %>%
 ungroup() %>%
 ggplot(aes(x=points, y=n, fill=points)) +
  geom_col() + facet_wrap(~sentiment) +
  guides(fill=F) + coord_flip() +theme_classic() + ylab('Number of Observation') + 
  xlab('Points') + ggtitle('Emotion') + 
  theme(plot.title = element_text(hjust = 0.5))

```


##2. Text Analysis
##3. Recommendation System

# The Results
## Interpretation
## Assummptions
## Limitations and Uncertainties
## Areas of Future Investigation

# References
[1]Bernard Chen, Valentin V., James P., and Travis A. Wineinformatics: A Quantitative Analysis of Wine Reviewers. <i> Fermentation </i>. 2018 <br>
[2]Quandt, R.E. A note on a test for the sum of ranksums. <i>J. Wine Econ</i>. 2007, 2, 98-102. <br>




