---
title: "Data Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r library, include=FALSE}
library(data.table)
library(DT)
library(tidyverse)
```


```{r read data, echo=FALSE}
dat <- fread(input = '../Data/winemag-data-130k-v2.csv',verbose = FALSE,na.strings=c(""))
```

```{r functions}
```


```{r functions}
percentage.table <- function(x, digits = 1){
  tab <- table(x)
  percentage.tab <- 100*tab/(sum(tab))
  rounded.tab <- round(x = percentage.tab, digits = digits)
  return(rounded.tab)
}

round.numerics <- function(x, digits){
  if(is.numeric(x)){
    x <- round(x = x, digits = digits)
  }
  return(x)
}
miss.value <- function(x){
  miss.rate <- round(100*mean(is.na(x)),2)
  return(miss.rate)
}

head(dat)
```


```{r constants}
country.name <- "country"
description.name <- "description"
designation.name <- "designation"
points.name <- "points"
price.name <- "price"
province.name <- "province"
region_1.name <- "region_1"
region_2.name <- "region_2"
taster.name <- "taster_name"
twitter.name <- "taster_twitter_handle" 
title.name <- "title"
variaty.name <- "variety"
winery.name <- "winery"

dat[,eval(points.name)] <- as.numeric(dat[,get(points.name)])
dat[,eval(price.name)] <- as.numeric(dat[,get(price.name)])

single.var <- c(points.name, price.name, country.name)
```


```{r percentage missing}
```


```{r percentage missing}
# transpose missing value per column 
tab <- t(dat[,lapply(X=.SD,FUN="miss.value")])
```


```{r percentage missing}
# conver to numeric 
tab2 <- data.table(var=names(dat),miss=as.numeric(tab))

# create a plot of all the missing rate 
barplot(height=tab2$miss, names.arg=tab2$var,space=0.01, las=1,
          main="Missing Rate",ylab="Percentage", ylim=c(0,100),col="dodgerblue")

  text(x = -0.5 + 1.02*1:tab2[, .N], y = -15, labels = tab2$var,srt = 45, cex = 1, pos = 2)
  space_val=0
  text(x=-0.4+1:length(tab)*(1+space_val),y=tab,labels=sprintf("%.1f%%",tab),pos=3)
```



```{r}
# unique twitter names 
levels(as.factor(dat$taster_twitter_handle))
levels(as.factor(dat$taster_name))

# remove twitter names 
 dat$taster_twitter_handle <- NULL
```


## Winery 
```{r}
winery.designation <- dat %>%
  select(designation,winery)
winery.designation[winery.designation$winery == ':Nota Bene',]
winery.designation %>%
  group_by(winery) %>%
  summarize(n = n())
```

We reseached wine designation to further understand Wine Designation and according to Napa Valley Vinters: 

Vineyard Designations Optional. Many wineries name the vineyard where the grapes were grown because the winery believes the property produces an unusually high-quality grape. The winery or an independent grower may own the vineyard. When using a vineyard designation on a wine label, federal regulations require that 95% of the grapes be grown in the named vineyard.

```{r}
# evaluate designation as no wine designation 
dat[is.na(get(designation.name)), eval('designation') := 'No Wine Designation']
```


# region 
```{r}
dat[is.na(get(region_1.name)), eval('region_1') := get(province.name)]
dat[is.na(get(region_2.name)), eval('region_2') := get(region_1.name)]

```


# Taster name 

```{r}
dat[is.na(get(taster.name)), eval('taster_name') := 'Anonymous']
```

# price 
```{r}
dat.final <- dat[complete.cases(dat)]

paste0( nrow(dat) - nrow(dat.final), ' rows were removed or ', round((nrow(dat) / nrow(dat.final) - 1) * 100,2),'%' , 'of the data')
```


```{r}
# transpose missing value per column 
tab <- t(dat.final[,lapply(X=.SD,FUN="miss.value")])
tab
```




```{r}
write.csv(dat.final, '../Data/wine.clean.csv')
```

Sources: https://napavintners.com/wines/how_to_read_a_wine_label.asp

https://winefolly.com/review/french-wine-labels-and-terms/ 

https://www.ttb.gov/pdf/brochures/p51901.pdf